---
title: "Quiz -  Lesson 7"
author: "Duncan Munslow"
date: "August 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#For Questions 1-5, consider the example of flipping a coin with unknown probability of heads (\thetaθ):

### Question 1

Suppose we use a Bernoulli likelihood for each coin flip, i.e., f(y_i \mid \theta) = \theta^{y_i} (1-\theta)^{1-y_i} I_{\{ 0 \le \theta \le 1 \}}f(y 
i
theta	 ∣θ)=θ 
y 
i
theta
 (1−θ) 
1−y 
i
theta
 I 
{0≤θ≤1}
theta	  for y_i=0y 
i
theta	 =0 or y_i = 1y 
i
theta	 =1, and a uniform prior for theta.
#### Answer: Beta(1 + 0, 1+4 - 0) = Beta(1,5)


### Question 2

Coin flip:

Which of the following graphs depicts the posterior PDF of theta if we observe the sequence (T, T, T, T)? (You may want to use R or Excel to plot the posterior.)


```{r pressure, echo=FALSE}
theta <- seq(from=0,to=1,by=.01)

plot(theta,dbeta(theta,1,5),type="l")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



## Question 3

What is the maximum likelihood estimate (MLE) of theta if we observe the sequence (T, T, T, T)?

#### Answer: 0/4 = 0

## Question 4

What is the posterior mean estimate of theta if we observe the sequence (T, T, T, T)? Round your answer to two decimal places.


Note: Mean of Beta(alpa, beta) = Alpha / Alpha + Beta

```{r posterior_mean}

1/6

```



## Question 5

Use R or Excel to find the posterior probability that theta <0.5 if we observe the sequence (T,T,T,T). Round your answer to two decimal places.

```{r posterier_prob}

pbeta(.5,1,5)
```


---

For Questions 6-9, consider the following scenario:

An engineer wants to assess the reliability of a new chemical refinement process by measuring theta, the proportion of samples that fail a battery of tests. These tests are expensive, and the budget only allows 20 tests on randomly selected samples. Assuming each test is independent, she assigns a binomial likelihood where XX counts the samples which fail. Historically, new processes pass about half of the time, so she assigns a Beta(2,2) prior for theta (prior mean 0.5 and prior sample size 4). The outcome of the tests is 6 fails and 14 passes.


## Question 6

What is the posterior distribution for theta?


#### Answer: Beta(2 + 6, 2+20-6) = Beta( 8, 16)


## Question 7

Use R or Excel to calculate the upper end of an equal-tailed 95% credible interval for theta. Round your answer to two decimal places.


```{r 95pctint}

qbeta(.975,8,16) 

# Question 8
qbeta(.025,8,16) > .3

```

## Question 8

The engineer tells you that the process is considered promising and can proceed to another phase of testing if we are 90% sure that the failure rate is less than .35.

Calculate the posterior probability P(theta <.35∣x). In your role as the statistician, would you say that this new chemical should pass?

``` {r post_prob}
pbeta(.35,8,16)
```

